Dark matter halo shape in the Auriga simulations: radial dependence, time evolution and correlation with baryon disk properties

### 2019-07-17 Document/paper.tex
caption 6 and 7

\begin{figure*}
\begin{center}
  \subfloat[DM shape at small radius]{\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_A_DM.pdf}} 
  \subfloat[DM shape at large radius]{\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_A_MHD.pdf}} 
\end{center}
\caption{}
\label{fig:triaxial_history_A}
\end{figure*}

\begin{figure*}
\begin{center}
  \subfloat[DM shape at small radius]{\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_B_DM.pdf}} 
  \subfloat[DM shape at large radius]{\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_B_MHD.pdf}} 
\end{center}
\caption{}
\label{fig:triaxial_history_B}
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_A_DM.pdf}
\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_A_MHD.pdf}
\end{center}
\caption{Axial ratios as a function of time (colour circles) and
  radius (dashed lines). 
  The left/right columns correspond to DMO/MHD simulations, respectively. 
  The colour indicates the redshift at which the shape was measured
  (always at $R_{200}$ at that time.)
  The radial shapes goes from $R_{200}$ down to $\sim 1$ kpc.
  These three halos correspond to a first half the sample for the \texttt{Level3}
  haloes. 
}
\label{fig:triaxial_history_A}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_B_DM.pdf}
\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_B_MHD.pdf}
\end{center}
\caption{Same as Figure \ref{fig:triaxial_history_A}.
  These three halos correspond the second half of the sample for the
  \texttt{Level3} haloes. 
}
\label{fig:triaxial_history_B}
\end{figure*}
